Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-12 p2/axioms.tex
Starting with the definition of domains

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
For example, we will write
$S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
% monoid, but not free monoid
% monoid: semigroup with identity element
% Sequences of commands form a free semigroup
Sequences of commands form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\eqext T$.
% preorder: reflexive and transitive
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

>>>>

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
For example, we will write
$S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
% monoid, but not free monoid
% monoid: semigroup with identity element
% Sequences of commands form a free semigroup
Sequences of commands form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$, which is the set of filesystems $S$ is defined on,
that is, which it does not break.

We write $\Img{S}$ to denote the image of the domain of the sequence $X$.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

### 2016-10-12 p2/works-inverse.tex
Introduction of partial functions
Starting with the definition of domains

\begin{mydef}[Sets of sequences]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
to denote such sets for brevity.
We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
\end{mydef}

\begin{mydef}[$\Dom{X}$ and $\Img{X}$]
$\Dom{X}$ is the domain of $X$.
For a sequence of commands $A$, $\Dom{A}$ is the set of filesystems $A$ does not break.
For a set of sequences $\seqset{A}$, $\Dom{\seqset{A}}$ is the set of filesystems no $A\in\seqset{A}$ breaks.
We write $\Img{X}$ to denote the image of the domain of the sequence $X$.
\end{mydef}

@@

>>>>

\begin{mydef}[Sets of sequences]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
to denote such sets for brevity.
We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$,
and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
\end{mydef}

@@

% TODO Commands/sequences are in fact partial (one-to-one) functions, and/or partial bijections. See
% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins
% https://en.wikipedia.org/wiki/Symmetric_inverse_semigroup
% https://en.wikipedia.org/wiki/Partial_function
